Context-dependent consequences of including lagged effects in demographic models

### 2022-05-25 docs/paper.Rmd
add a paragraph and some results for the time it takes to iterate the IPMs (#1)

>>>>

The time to iterate the DLNM models is much higher than than deterministic and kernel-resampled.
The greater use of computational resources is likely a result of `predict()` being much slower for GAMs with 2D smooths because the number of knots is much higher compared to the GAMs used for the vital rates models in the determinsitic and kernel-resampled IPMs.
<!--# also note that this can't really be paralellized because each iteration depends on the previous one.  There's *maybe* some potential speed gains in using multiple cores with predict.bam(), but unlikely to be substantial. -->

```{r}
meta_df <- 
  tar_meta() %>% 
  select(name, size, bytes, time, seconds) %>% 
  filter(str_detect(name, "^ipm_\\w+_[cf]{2}$")) %>% 
  mutate(minutes = seconds / 60,
         hours = minutes / 60)

meta_df %>% 
  separate(name, into = c("trash", "IPM", "Habitat")) %>% 
  select(-trash) %>% 
  select(IPM, Habitat, minutes) %>% 
  group_by(IPM) %>% 
  summarize(mean_time_min = round(mean(minutes), 2))
```
